\begin{center}
  \nrp 1  
  {\LARGE \hlc[___gray]{The Archive}}\\
  \vspace{10pt}
  \large 
  \href{https://rish987.github.io/}{\tt {rish987.github.io}}\\
\end{center}
\begin{part}{Introduction}
  \nrp 2 
  This is my personal archive,
  a place where I plan to record
  what I've learned in the fields of 
  mathematics, computer science, and more.

  A continual work in progress, the intent is 
  for it to be a completely self-contained repository,
  with descriptions that are as concise as physically possible.

  The archive is free and open-source, 
  together with the archiver, the tool I use to build archives.
  You can find them below:

  \href{https://github.com/rish987/archive}{\tt github.com/rish987/archive}

  \href{https://github.com/rish987/archiver}{\tt github.com/rish987/archiver}.

\end{part}

\begin{part}{Navigation}
  \nrp 3 
  It's organized hierarchically into units called ``\refr{}s,''
  which can be one of the following types:
  \begin{itemize}
    \item \nrp 4  ``\refroot.'' The \refr\ you're currently on!
      There's only one \refr\ of this type. 
      It's reserved for descriptions that apply to the entire archive.
    \item \nrp 5  ``\tpc{}'' (denoted by \topicd). These repeat a general format:
    \begin{itemize}
      \item Describe a simple concept that relies on a simple physical intuition.
      \item Correspond this intuition with some initial notation, and 
        possibly define some more notation using this initial notation.
      \item Use this notation to describe some facts that follow from it.
        These facts are merely stated, not proven.
    \end{itemize}
    \item \nrp 6  ``\defn'' (denoted by \definitiond). 
      These introduce notation that depend on a previously described
      physical intuition, previously defined notation, or a combination of both.
    \item \nrp 7  ``\proofl{}'' (denoted by \proofd). 
      These state a fact and show why it is true, using previously defined notation.
    \item \nrp 8  ``\notel{}'' (denoted by \noted). 
      These may be one of the following:
      \begin{itemize}
        \item A visual/verbal interpretation of a concept that isn't strictly 
          necessary for understanding, but could be helpful.
        \item A temporary stand-in for a \refr\ that will be properly integrated 
          into its own topic at a later time.
      \end{itemize}
  \end{itemize}

  \nrp 9 
  Each \refr\ is delimited by a pair of horizontal rules.

  \nrp 10 
  At the upper-left corner of each \refr\ is a ``\refrnum'' (``RN'' for short),
  a unique ID that will never, ever change. 
  When verbally referring to a particular \refr, we say ``RN'' followed by 
  the \refrnum, e.g. ``RN53.'' 
  The numbers themselves don't actually mean anything,
  other than roughly tracking the order in which I created the \refr{}s.
  In fact, some \refrnum{}s may not actually exist, if I decided to delete its former \refr!

  \nrp 11 
  In the margins of a reference are labels for ``\refrp{}s'' and their
  associated ``\refrpnum{}s.''
  These are logical sections of the \refr\ that should 
  be verbally referred with ``RNP'' followed by 
  the \refrnum, a period, and the \refrpnum, e.g. ``RNP53.3.'' to indicate \refrp\ 3 of \refr\ 53.
  Similarly to \refrnum{}s, the \refrpnum{}s themselves don't mean anything
  other than roughly tracking the order in which I created them.

  \nrp 12 
  The symbol \colorbox{__gray}{\tt \color{red} >} denotes a link to a YouTube video for that reference.
  It should never be strictly necessary to watch the video to understand the reference,
  as all the details should be in the text.

  \nrp 13 
  At the upper-right corner of each \refr\ is a ``\refrpat,'' 
  a unique path that identifies this \refr's place in the hierarchy of \refr{}s.
  It's written in UNIX-SHELL path style.

  \nrp 14 
  A \refr\ is linked to either explicitly or implicitly.
  These links may either be ``local'' or ``global.'' 
  The difference is contextual -- the 
  first link to a \refr\ in the hierarchy
  is a ``local'' link, in that following it will append to the current \refrpat.
  All other links are ``global,'' in that the current \refrpat\ has
  no relation to that of the linked \refr.
  \begin{itemize}
    \item \nrp 15  An explicit link has the form \exampleln.
    \item \nrp 16  An implicit link is present in the notation, 
      and links to the \refr\ where the notation was originally defined.
      Just as notation is nested, so too are the corresponding implicit links.

      We follow the convention that implicit links are always global;
      it follows that the first link to a \refr\ is always explicit.
  \end{itemize}
\end{part}

\begin{part}{Annotations}
  \nrp 17 
  Equations may be annotated as, for example:
  $$a \rellr = x i b \rell = y c \rellr {\ge} z j d,$$
  followed by
  $$g \relr = {(x-z)->\exampleln} h,$$
  where blue underset boxes define ``\labell{}s,''
  and grey overset boxes provide ``\explnl{}s'' that explain why an (in)equality follows, 
  using previously defined \labell{}s and other \refr{}s.
  An \explnl\ is formatted as follows:
  \begin{itemize}
    \item \nrp 18  {\tt x} indicates to consider the single (in)equality labeled by {\tt x}.

      In the example above, {\tt x} refers to $a = b$.
    \item \nrp 19  {\tt (x-y)} indicates that, when {\tt x} and {\tt y} appear in a chain (in)equality,
      to consider the equation that results from cropping out what appears 
      in between the (in)equalities labeled by {\tt x} and {\tt y}.

      In the example above, {\tt(x-z)} refers to $a \ge d$.
    \item \nrp 20  {\tt x->\exampleln} indicates to use (in)equality {\tt x}
      as the antecendent of the \refr\ linked to by \exampleln.

      In the example above, {\tt(x-z)->\exampleln} refers to use $a \ge d$
      as an antecedent of the \refr\ with RN {\tt[RN]}.
  \end{itemize}
  \nrp 29 Where an \explnl\ is not provided, the result should follow from simple algebra or arithmetic.

  \nrp 21 
  Note that \refrpat{}s and \labell{}s are simply meant to be unique, memorable identifiers, and by themselves don't actually matter. 
  Though technically, they always are acronyms/abbreviations of {\it something} --
  see if you can figure out what they are in the YouTube video comments!
\end{part}

\begin{part}{Formats}
  \nrp 22 
  The archive is available in the following formats:
  \begin{itemize}
    \item \nrp 23  \href{https://rish987.github.io/files/archives/tree_online/archive/tree_online.pdf}{\tt {tree\_online}}:
      Each \refr\ has its own online link in a ``\refr\ tree'' and corresponding PDF. 
      
      Links are online hyperlinks.
    \item \nrp 24  \href{https://rish987.github.io/files/archives/tree/archive.tar.gz}{\tt {tree}}:
      Local download of the \refr\ tree.

      Links are remote PDF links.
    \item \nrp 25  \href{https://rish987.github.io/files/archives/full/archive/full.pdf}{\tt {full}}:
      All \refr{}s are combined into a single PDF, ordered by depth (i.e., a linearized DAG),
      where each \refr\ starts on a new page.

      Links are cross-referencing links within the same PDF.
    \item \nrp 26  \href{https://rish987.github.io/files/archives/full_compact/archive/full_compact.pdf}{\tt {full\_compact}}:
      Identical to {\tt full}, except \refr{}s may start on the same page.

      Links are cross-referencing links within the same PDF.
  \end{itemize}

  \nrp 27 
  For the best experience, I highly recommend using \href{https://mozilla.github.io/pdf.js/}{\tt pdf.js} 
  (native to the \href{https://www.mozilla.org/en-US/firefox/new/}{Firefox web browser},
  but also \href{https://chrome.google.com/webstore/detail/pdf-viewer/oemmndcbldboiebfnladdacbdfmadadm}{available on Chrome})
  as your PDF viewer, in ``presentation mode'' ({\tt ctrl+alt+p}) on a vertical monitor.
  Note that with {\tt pdf.js}, you can use your browser's history navigation functionality
  to traverse your link history ({\tt alt+rightarrow} and {\tt alt+leftarrow}).

  \nrp 28 
  For offline viewing, I highly recommend 
  \href{http://manpages.ubuntu.com/manpages/xenial/man1/atril.1.html}{Atril Document Viewer}.
\end{part}

\begin{part}{Topics}
\refln{topic}{prob}{Probability Theory}
\end{part}
